PyUltraLight: A Pseudo-Spectral Solver for Ultralight Dark Matter Dynamics

### 2018-06-14 draft.tex
One more small edit.

where $H=\Dot{a}(t)/a(t)$. At late times in an expanding universe, $H\ll m$ \sh{I might be confused, but I'm reasonably sure the approximation is $H\ll m/\hbar$} and it is sufficient to set $H=0$ and $a(t)=1$ in equation \ref{eq:linear}. This is a good approximation even at relatively high redshifts, including the epochs of early structure formation\sh{maybe worth mention that this approximation is equivalent to saying that the Hubble horizon is much larger than the compton wavelength? - I'm not sure this condition is enough to neglect H though because in Nathan's code it is still true, but H is being included. It is somehow the de Broglie wavelength that is relevant, not just Compton, so a comparison also needs made to the $\nabla^2 \phi$ term}. Alternatively, if we consider a non-expanding universe, these equalities are true by definition. In either case, we can remove the third term in equation \ref{eq:linear}. The resulting equation can then be analysed using WKB methods in the non-relativistic regime \footnote{For a detailed explication of the WKB approximation in the non-relativistic limit, see \cite{Young2015}.}. This allows us to write an ansatz solution for the field $\phi$:

>>>>

where $H=\Dot{a}(t)/a(t)$. At late times in an expanding universe, $H\ll m/\hbar$ and it is sufficient to set $H=0$ and $a(t)=1$ in equation \ref{eq:linear}. This is a good approximation even at relatively high redshifts, including the epochs of early structure formation\sh{maybe worth mention that this approximation is equivalent to saying that the Hubble horizon is much larger than the compton wavelength? - I'm not sure this condition is enough to neglect H though because in Nathan's code it is still true, but H is being included. It is somehow the de Broglie wavelength that is relevant, not just Compton, so a comparison also needs made to the $\nabla^2 \phi$ term}. Alternatively, if we consider a non-expanding universe, these equalities are true by definition. In either case, we can remove the third term in equation \ref{eq:linear}. The resulting equation can then be analysed using WKB methods in the non-relativistic regime \footnote{For a detailed explication of the WKB approximation in the non-relativistic limit, see \cite{Young2015}.}. This allows us to write an ansatz solution for the field $\phi$:
